\documentclass[11 pt, a4paper]{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Load Packages %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[hmargin=1.25in,vmargin=1.25in]{geometry}
\usepackage{amsmath,amssymb,amsthm,mathrsfs,amsfonts,mathtools}
\usepackage{tabularx,siunitx,makecell,booktabs,colortbl,threeparttable,multirow}
\usepackage[dvipsnames,svgnames, x11names]{xcolor}% Must load before tikz
\usepackage{enumitem,setspace,caption,natbib}
\usepackage{verbatim,listings,xurl}
\usepackage[nomessages]{fp}
\usepackage{float}
%\usepackage{pythontex}
\usepackage[hyperindex,breaklinks]{hyperref}      % hyperindex,breaklinks needed for arXiv
\usepackage[open,openlevel=2,numbered]{bookmark}  % Must load after hyperref
\usepackage{tikz,pgfplots,pgfplotstable}
\pgfplotsset{compat=1.11}
\usetikzlibrary{positioning,automata,decorations.markings,decorations.pathreplacing}
\usetikzlibrary{arrows,arrows.meta}
\usetikzlibrary{shapes.geometric} % For creating stars
\usetikzlibrary{colorbrewer}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Customized Settings %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Renew commands
\renewcommand{\bibname}{References}
\renewcommand{\qedsymbol}{$\blacksquare$}
% Length and spacing
\onehalfspacing
\setlength{\bibsep}{0.25pt}
\makeatletter
\renewcommand\paragraph{\@startsection{paragraph}{4}{\z@}%
            {-2.5ex\@plus -1ex \@minus -.25ex}% Space before sectioning title
            {1.25ex \@plus .25ex}             % Space after sectioning title
            {\normalfont\normalsize\bfseries}}
\makeatother
\parskip = 1.2ex plus 0.5 ex minus0.2 ex
% Links
\hypersetup{colorlinks, linkcolor = {NavyBlue}, citecolor = {NavyBlue}, urlcolor ={NavyBlue}}
\setlength{\abovecaptionskip}{3pt plus 1pt minus 2pt}
\captionsetup[table]{belowskip=2.5ex}
\setdisplayskipstretch{0.8}

\begin{document}
\title{\vspace*{-2cm}\sc \mbox{\Large Econ 522 -- Problem Set 2}}
\date{\vspace*{-1.5cm}Due --- TBD}
\maketitle
\vspace*{-1cm}


\begin{enumerate}
  \item Let $\{Y_i,Z_i\}_{i=1}^n$ be an i.i.d.\ sample generated by: for some $\theta_0\in\Theta\subset\mathbf R^k$,
  \begin{align}
  Y = g(Z,\theta_0)+ U~,
  \end{align}
  where $E[U|Z]=0$ and $g: \mathcal Z\times\Theta\to\mathbf R$ is a known map.
  \begin{enumerate}
    \item Define $Q_0(\theta)=E[(Y-g(Z,\theta))^2]$. Derive a condition under which $Q_0(\theta)$ has a unique minimizer $\theta_0\in\Theta$.
    \item Formalize conditions under which $\hat\theta_n\overset{p}{\to}\theta_0$ and provide a proof.
    \item Formalize conditions under which $\hat\theta_n$ is asymptotically normal and provide a proof. You may directly assume $\hat\theta_n\overset{p}{\to}\theta_0$.
  \end{enumerate}

  \item Consider the criterion function (2.29) in the lecture notes. The M-estimation theory implies that the MLE $\hat\theta_n$ is asymptotically normal under regularity conditions.
  \begin{enumerate}
    \item Derive the asymptotic variance of $\hat\theta_n$ that is robust to model misspecification.
    \item Suppose that $G$ is the standard logistic cdf. The odds ratio then equals $\exp\{z_0^\intercal\theta_0\}$ at a particular covariate $z_0$. Propose an estimator for it and derive the asymptotic variance of the estimator.
    \item Propose an estimator for the asymptotic variance in part (b).
  \end{enumerate}

  \item Let $\{Y_{1i}, Y_{2i},Z_i\}_{i=1}^n$ be an i.i.d.\ sample generated by
  \begin{align}
   Y_{1i}&=\max\{Z_{1i}^\intercal\beta_0+Y_{2i}\gamma_0+U_i,0\}~,\label{Eqn: LDV, censoring endogeneity}\\
   Y_{2i}&=Z_i^\intercal \pi_0+V_i~,
   \end{align}
   where $Z_i$ is independent of $(U_i,V_i)$ and contains $Z_{1i}$ as a subvector, and $(U_i,V_i)^\intercal$ is bivariate normal with mean zero and variance
   \[
   \begin{bmatrix}
   \sigma_u^2 & \sigma_{uv}\\
   \sigma_{vu} & \sigma_v^2
   \end{bmatrix}~.
   \]
   Thus, this is just the censored regression with an endogenous regressor $Y_{2i}$.
   \begin{enumerate}
     \item Define $\epsilon_i\equiv U_i-\sigma_{uv}\sigma_v^{-2} V_i$. Show that $V_i$ and $\epsilon_i$ are independent.
     \item Plugging $U_i=\epsilon_i+\sigma_{uv}\sigma_v^{-2} V_i$ into \eqref{Eqn: LDV, censoring endogeneity} to obtain
     \begin{align}
      Y_{1i}=\max\{Z_{1i}^\intercal\beta_0+Y_{2i}\gamma_0+\sigma_{uv}\sigma_v^{-2}V_i+\epsilon_i,0\}~.
     \end{align}
     Suppose for the moment that we observe $V_i$. How would you estimate $\beta_0$ and $\gamma_0$? Justify your proposal.

     \item Now back to the reality where we actually do not observe $V_i$. How would you estimate $\beta_0$ and $\gamma_0$?

   \end{enumerate}

  \item Do Exercise 26.12 in Hansen (2022).

\end{enumerate}


\end{document}
